---
title: "May-3-ggplot"
author: "Min-Yao"
date: "2017年5月1日"
output: 
  html_document: 
    keep_md: yes
---

## 3.6 Geometric objects

```{r}
library(ggplot2)
```


```{r}
# left
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

# right
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy))

ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv))

ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv, color = drv)) +
  geom_point(mapping = aes(x = displ, y = hwy, color = drv))

```

```{r}
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
              
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv))
    
ggplot(data = mpg) +
  geom_smooth(
    mapping = aes(x = displ, y = hwy, group = drv)
  )

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy))

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth()

#ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
#  geom_point(mapping = aes(color = class)) + 
#  geom_smooth(data = filter (mpg, class == "subcompact"), se = FALSE)
```

### 3.6.1 Exercises

```{r}

#2
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)

#5
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

#6
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy), se = FALSE)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv), se = FALSE)

ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, color = drv), se = FALSE) +
  geom_point(mapping = aes(x = displ, y = hwy, color = drv))

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(se = FALSE) +
  geom_point(mapping = aes(color = drv))

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(mapping = aes(group = drv, linetype = drv), se = FALSE) +
  geom_point(mapping = aes(color = drv))


ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = drv, stroke = 2))
```

>1. a line chart:  `geom_curve()`. A boxplot: `geom_boxplot()`. A histogram: `geom_histogram()`. An area chart: `geom_area(stat = "bin")`.

>3. show.legend: logical. Should this layer be included in the legends? NA, the default, includes if any aesthetics are mapped. FALSE never includes, and TRUE always includes.`show.legend = FALSE` will not show the legend labels. If you remove it, it will show the legend labels. You used it earlier in the chapter because you don't need the legend labels.

>4. se: display confidence interval around smooth (TRUE by default, see level to control.

>5. No, these two graphs look the same. By passing a set of mappings to ggplot(), ggplot2 will treat these mappings as global mappings that apply to each geom in the graph. In other words, this code will produce the same plot as the previous code.




