---
title: "Exploratory Data Analysis, cont Tibbles"
author: "Min-Yao"
date: "2017年5月29日"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(ggplot2)
library(tidyverse)
library(modelr)
```


## 7.6 Patterns and models

```{r}
ggplot(data = faithful) + 
  geom_point(mapping = aes(x = eruptions, y = waiting))

#library(modelr)

mod <- lm(log(price) ~ log(carat), data = diamonds)

diamonds2 <- diamonds %>% 
  add_residuals(mod) %>% 
  mutate(resid = exp(resid))

ggplot(data = diamonds2) + 
  geom_point(mapping = aes(x = carat, y = resid))

ggplot(data = diamonds2) + 
  geom_boxplot(mapping = aes(x = cut, y = resid))
```


## 7.7 ggplot2 calls

```{r}
ggplot(data = faithful, mapping = aes(x = eruptions)) + 
  geom_freqpoly(binwidth = 0.25)

ggplot(faithful, aes(eruptions)) + 
  geom_freqpoly(binwidth = 0.25)

diamonds %>% 
  count(cut, clarity) %>% 
  ggplot(aes(clarity, cut, fill = n)) + 
    geom_tile()
```

## 7.8 Learning more


# 8 Workflow: projects

## 8.1 What is real?

## 8.2 Where does your analysis live?

```{r}
getwd()
```


## 8.3 Paths and directories


## 8.4 RStudio projects

```{r}
library(tidyverse)

ggplot(diamonds, aes(carat, price)) + 
  geom_hex()
ggsave("diamonds.pdf")

write_csv(diamonds, "diamonds.csv")
```


## 8.5 Summary

# 10 Tibbles

## 10.1 Introduction

### 10.1.1 Prerequisites

```{r}
library(tidyverse)

```


## 10.2 Creating tibbles

```{r}
as_tibble(iris)

tibble(
  x = 1:5, 
  y = 1, 
  z = x ^ 2 + y
)

tb <- tibble(
  `:)` = "smile", 
  ` ` = "space",
  `2000` = "number"
)
tb

tribble(
  ~x, ~y, ~z,
  #--|--|----
  "a", 2, 3.6,
  "b", 1, 8.5
)

```

## 10.3 Tibbles vs. data.frame

### 10.3.1 Printing

```{r}

library(lubridate)

tibble(
  a = lubridate::now() + runif(1e3) * 86400,
  b = lubridate::today() + runif(1e3) * 30,
  c = 1:1e3,
  d = runif(1e3),
  e = sample(letters, 1e3, replace = TRUE)
)

nycflights13::flights %>% 
  print(n = 10, width = Inf)

nycflights13::flights %>% 
  View()
```


### 10.3.2 Subsetting

```{r}
df <- tibble(
  x = runif(5),
  y = rnorm(5)
)

df$x

df[["x"]]

df[[1]]

df %>% .$x

df %>% .[["x"]]

```


## 10.4 Interacting with older code

```{r}
class(as.data.frame(tb))

```


## 10.5 Exercises

1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).
```{r}

mtcars
as_tibble(mtcars)

class(mtcars)
class(as_tibble(mtcars))
```

2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

df2 <- tibble(abc = 1, xyz = "a")
df2$x
df2[, "xyz"]
df2[, c("abc", "xyz")]
```


3. If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

```{r}
mpg




```


4. Practice referring to non-syntactic names in the following data frame by:

```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```


Extracting the variable called 1.
```{r}
annoying$`1`
```


Plotting a scatterplot of 1 vs 2.
```{r}
ggplot(annoying, aes(x=`1`, y=`2`)) +
    geom_point() 

```

Creating a new column called 3 which is 2 divided by 1.

```{r}
annoying2 <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`)),
  `3` = `2` / `1`
)
annoying2
```


Renaming the columns to one, two and three.

```{r}
annoying3 <- tibble(
  one = 1:10,
  two = one * 2 + rnorm(length(one)),
  three = two / one
)
annoying3
```


5. What does tibble::enframe() do? When might you use it?

```{r}
?enframe()
enframe(1:3)
enframe(c(a = 5, b = 7))
```

> A helper function that converts named atomic vectors or lists to two-column data frames. For unnamed vectors, the natural sequence is used as name column.
> enframe(x, name = "name", value = "value")

6. What option controls how many additional column names are printed at the footer of a tibble?

```{r}
package?tibble
```

tibble.print_max
Row number threshold: Maximum number of rows printed. Set to Inf to always print all rows. Default: 20.

tibble.print_min
Number of rows printed if row number threshold is exceeded. Default: 10.

tibble.width
Output width. Default: NULL (use width option).

tibble.max_extra_cols
Number of extra columns printed in reduced form. Default: 100.