---
title: "Lab 2"
author: "Min-Yao"
date: "2017?~11??28??"
output: 
  html_document: 
    keep_md: yes
---
# Chapter 2 Lab: Introduction to R
```{r}
# Chapter 2 Lab: Introduction to R

library(ISLR)
head(Auto)

# Basic Commands

x <- c(1,3,2,5)
x
x = c(1,6,2)
x
y = c(1,4,3)
length(x)
length(y)
x+y
ls()
rm(x,y)
ls()
rm(list=ls())
#?matrix
x=matrix(data=c(1,2,3,4), nrow=2, ncol=2)
x
x=matrix(c(1,2,3,4),2,2)
matrix(c(1,2,3,4),2,2,byrow=TRUE)
sqrt(x)
x^2
x=rnorm(50)
y=x+rnorm(50,mean=50,sd=.1)
cor(x,y)
set.seed(1303)
rnorm(50)
set.seed(3)
y=rnorm(100)
mean(y)
var(y)
sqrt(var(y))
sd(y)
```
# Graphics
```{r}
# Graphics

x=rnorm(100)
y=rnorm(100)
plot(x,y)
plot(x,y,xlab="this is the x-axis",ylab="this is the y-axis",main="Plot of X vs Y")
pdf("Figure.pdf")
plot(x,y,col="green")
dev.off()
x=seq(1,10)
x
x=1:10
x
x=seq(-pi,pi,length=50)
y=x
f=outer(x,y,function(x,y)cos(y)/(1+x^2))
contour(x,y,f)
contour(x,y,f,nlevels=45,add=T)
fa=(f-t(f))/2
contour(x,y,fa,nlevels=15)
image(x,y,fa)
persp(x,y,fa)
persp(x,y,fa,theta=30)
persp(x,y,fa,theta=30,phi=20)
persp(x,y,fa,theta=30,phi=70)
persp(x,y,fa,theta=30,phi=40)
```
# Indexing Data
```{r}
# Indexing Data

A=matrix(1:16,4,4)
A
A[2,3]
A[c(1,3),c(2,4)]
A[1:3,2:4]
A[1:2,]
A[,1:2]
A[1,]
A[-c(1,3),]
A[-c(1,3),-c(1,3,4)]
dim(A)
```
# Loading Data
```{r}
# Loading Data

Auto=read.table("Auto.data")
#fix(Auto)
Auto=read.table("Auto.data",header=T,na.strings="?")
#fix(Auto)
Auto=read.csv("Auto.csv",header=T,na.strings="?")
#fix(Auto)
dim(Auto)
Auto[1:4,]
Auto=na.omit(Auto)
dim(Auto)
names(Auto)
```
# Additional Graphical and Numerical Summaries
```{r}
# Additional Graphical and Numerical Summaries

#plot(cylinders, mpg)
plot(Auto$cylinders, Auto$mpg)
attach(Auto)
plot(cylinders, mpg)
cylinders=as.factor(cylinders)
plot(cylinders, mpg)
plot(cylinders, mpg, col="red")
plot(cylinders, mpg, col="red", varwidth=T)
plot(cylinders, mpg, col="red", varwidth=T,horizontal=T)
plot(cylinders, mpg, col="red", varwidth=T, xlab="cylinders", ylab="MPG")
hist(mpg)
hist(mpg,col=2)
hist(mpg,col=2,breaks=15)
pairs(Auto)
pairs(~ mpg + displacement + horsepower + weight + acceleration, Auto)
plot(horsepower,mpg)
identify(horsepower,mpg,name)
```


# 9.(a)
> quan: mpg, acceleration, weight, horsepower, displacement
> qual: origin, year, cylinders

# 9.(b,C)

```{r}
summary(Auto)
```

```{r}
str(Auto)
summary(mpg)

range(mpg)
range(acceleration)
range(displacement)
range(horsepower)
range(weight)

sd(mpg)
sd(acceleration)
sd(displacement)
sd(horsepower)
sd(weight)
```

# 9.(d)
```{r}
new.Auto = Auto[-c(10:85),]
#new.Auto
#Auto

summary(Auto)
summary(new.Auto)

range(new.Auto$mpg)
range(new.Auto$acceleration)
range(new.Auto$displacement)
range(new.Auto$horsepower)
range(new.Auto$weight)

sd(new.Auto$mpg)
sd(new.Auto$acceleration)
sd(new.Auto$displacement)
sd(new.Auto$horsepower)
sd(new.Auto$weight)
```

# 9.(e)
```{r}
#9.(e)
plot(cylinders, mpg, xlab="cylinders", ylab="MPG")
plot(displacement, mpg, xlab="displacement", ylab="MPG")
plot(horsepower, mpg, xlab="horsepower", ylab="MPG")
plot(weight, mpg, xlab="weight", ylab="MPG")
plot(acceleration, mpg, xlab="acceleration", ylab="MPG")
plot(year, mpg, xlab="year", ylab="MPG")
plot(origin, mpg, xlab="origin", ylab="MPG")

```
# 9.(f)
> The cars with lower displacement, horsepower, weight have higher gas mileage (mpg). 

# 10.(a)
```{r}
#10.
#(a)
library (MASS)
#Boston
#?Boston
summary(Boston)
str(Boston)
dim(Boston)
```
> 506 rows and 14 columns

>This data frame contains the following columns:

crim
per capita crime rate by town.

zn
proportion of residential land zoned for lots over 25,000 sq.ft.

indus
proportion of non-retail business acres per town.

chas
Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).

nox
nitrogen oxides concentration (parts per 10 million).

rm
average number of rooms per dwelling.

age
proportion of owner-occupied units built prior to 1940.

dis
weighted mean of distances to five Boston employment centres.

rad
index of accessibility to radial highways.

tax
full-value property-tax rate per \$10,000.

ptratio
pupil-teacher ratio by town.

black
1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.

lstat
lower status of the population (percent).

medv
median value of owner-occupied homes in \$1000s.

# 10(b-c)
```{r}
#(b)
pairs(Boston)
#(c)
attach(Boston)
plot(zn, crim, xlab="zn", ylab="crim")
plot(indus, crim, xlab="indus", ylab="crim")
plot(chas, crim, xlab="chas", ylab="crim")
plot(nox, crim, xlab="nox", ylab="crim")
plot(rm, crim, xlab="rm", ylab="crim")
plot(age, crim, xlab="age", ylab="crim")
plot(dis, crim, xlab="dis", ylab="crim")
plot(rad, crim, xlab="rad", ylab="crim")
plot(tax, crim, xlab="tax", ylab="crim")
plot(ptratio, crim, xlab="ptratio", ylab="crim")
plot(black, crim, xlab="black", ylab="crim")
plot(lstat, crim, xlab="lstat", ylab="crim")
plot(medv, crim, xlab="medv", ylab="crim")
```

#10(d-h)

```{r}
#(d)
summary(Boston$crim)
range(Boston$crim)
summary(Boston$tax)
range(Boston$tax)
summary(Boston$ptratio)
range(Boston$ptratio)
#(e)
as.data.frame(table(Boston$chas))

#(f)
summary(Boston$ptratio)
#(g)
summary(Boston$medv)
range(Boston$medv)
as.data.frame(table(Boston$medv))
min(Boston$medv)
attach(Boston)
newBoston <- Boston[order(medv),] 
newBoston
#(h)
as.data.frame(table(Boston$rm))
library(plyr)
count(which(Boston$rm > 7))
Bostonrm7 <- subset(Boston, rm > 7)
Bostonrm7
Bostonrm8 <- subset(Boston, rm > 8)
Bostonrm8

```

