---
title: "R-club-May-10"
author: "Min-Yao"
date: "2017年5月7日"
output: 
  html_document: 
    keep_md: yes
---

# 5 Data transformation

## 5.1 Introduction

### 5.1.1 Prerequisites

```{r}
library(nycflights13)
library(tidyverse)
```

### 5.1.2 nycflights13

```{r}
flights
View(flights)

```

### 5.1.3 dplyr basics

## 5.2 Filter rows with filter()
```{r}
filter(flights, month == 1, day == 1)
jan1 <- filter(flights, month == 1, day == 1)
(dec25 <- filter(flights, month == 12, day == 25))

```

### 5.2.1 Comparisons

```{r}
sqrt(2) ^ 2 == 2
1/49 * 49 == 1

near(sqrt(2) ^ 2,  2)
near(1 / 49 * 49, 1)
```

### 5.2.2 Logical operators

```{r}
filter(flights, month == 11 | month == 12)
nov_dec <- filter(flights, month %in% c(11, 12))

filter(flights, !(arr_delay > 120 | dep_delay > 120))
filter(flights, arr_delay <= 120, dep_delay <= 120)
```

### 5.2.3 Missing values

```{r}
NA > 5
10 == NA
NA + 10
NA / 2

NA == NA
x <- NA
y <- NA
x == y

is.na(x)

df <- tibble(x = c(1, NA, 3))
filter(df, x > 1)
filter(df, is.na(x) | x > 1)
```

### 5.2.4 Exercises

1.
```{r}
#1
?flights
airlines
##1
filter(flights, dep_delay >= 120)
##2
filter(flights, dest == "IAH" | dest == "HOU")
##3
filter(flights, carrier == "AA" | carrier == "UA" | carrier == "DL")
##4
filter(flights, month %in% c(7, 8, 9))
filter(flights, month %in% 7:9)
##5
filter(flights, arr_delay > 120 & dep_delay <= 0)
##6
filter(flights, dep_delay >= 60 & dep_delay - arr_delay > 30)
##7
filter(flights, dep_time == 2400 | dep_time <= 0600)
summary(flights)
       
```

2.
```{r}
#2
?between()

##7
filter(flights, between(dep_time, 0000, 0600))
```

> This is a shortcut for x >= left & x <= right, implemented efficiently in C++ for local values, and translated to the appropriate SQL for remote tables. between(x, left, right). Yes.

3.
```{r}
filter(flights, is.na(dep_time))
```

4.
```{r}
NA ^ 0
NA | TRUE
NA | 2
FALSE & NA
NA * 0
Inf*0

#
test<-c(3:6, NA)
test^0
test<-c(3:6, NA, "blue")
```

## 5.3 Arrange rows with arrange()


```{r}
arrange(flights, year, month, day)
arrange(flights, desc(arr_delay))

df <- tibble(x = c(5, 2, NA))
arrange(df, x)

arrange(df, desc(x))
```

### 5.3.1 Exercises

1.How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).
```{r}
df <- tibble(x = c(5, 2, NA))
arrange(df, x)
arrange(df, desc(is.na(x)))
arrange(df, desc(is.na(x)), x)
```

2.Sort flights to find the most delayed flights. Find the flights that left earliest.
```{r}
arrange(flights, desc(arr_delay))
arrange(flights, dep_delay)
```

3. Sort flights to find the fastest flights.
```{r}
arrange(flights, air_time)
```

4. Which flights travelled the longest? Which travelled the shortest?
```{r}
arrange(flights, distance)
arrange(flights, desc(distance))
```

## 5.4 Select columns with select()

```{r}
select(flights, year, month, day)
select(flights, year:day)
select(flights, -(year:day))

rename(flights, tail_num = tailnum)#new#old
select(flights, time_hour, air_time, everything())

```

### 5.4.1 Exercises

1. Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
head(select(flights, starts_with("dep"), starts_with("arr")),1)
head(select(flights, dep_time, dep_delay, arr_time, arr_delay),1)
head(select(flights, dep_time:arr_delay, -starts_with("sched")),1)
select(flights, matches("^(dep|arr)"))
```

2. What happens if you include the name of a variable multiple times in a select() call?
```{r}
select(flights, dep_time, dep_time)

```

> only select once

3.What does the one_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
?one_of()
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars))
```

> one_of(): variables in character vector.

4.Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?

```{r}
select(flights, contains("TIME"))
select(flights, contains("TIME", ignore.case = FALSE))
```

> surprise! because normaly R is sensetive to case.

## 5.5 Add new variables with mutate()

```{r}
flights_sml <- select(flights, 
  year:day, 
  ends_with("delay"), 
  distance, 
  air_time
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  speed = distance / air_time * 60
)


mutate(flights_sml,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)

transmute(flights,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
```

### 5.5.1 Useful creation functions

```{r}
transmute(flights,
  dep_time,
  hour = dep_time %/% 100,
  minute = dep_time %% 100
)

(x <- 1:10)
lag(x)
lead(x)
z <- c(2, 5, 9)
lag(z)
#shif one position

x
cumsum(x)
cummean(x)

y <- c(1, 2, 2, NA, 3, 4)
min_rank(y)
min_rank(desc(y))

row_number(y)
dense_rank(y)
percent_rank(y)
cume_dist(y)
```

### 5.5.2 Exercises

1. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
transmute(flights,
  dep_time,
  dep_time_hour = dep_time %/% 100,
  dep_time_minute = dep_time %% 100,
  dep_time_min = (dep_time_hour * 60) + dep_time_minute,
  sched_dep_time,
  sched_dep_time_hour = sched_dep_time %/% 100,
  sched_dep_time_minute = sched_dep_time %% 100,
  sched_dep_time_min = (sched_dep_time_hour * 60) + sched_dep_time_minute
  )
```

2.Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?
```{r}
transmute(flights,
          air_time,
          new_air_time = arr_time - dep_time
)

#
ggplot(flights, aes(x=air_time, y = (arr_time-dep_time))) + geom_point(alpha=.1)

#
flights2 <- transmute(flights, arr_time, dep_time, air_time, 
                      arr_time2 = arr_time %/% 100 * 60 + arr_time %% 100,
                      dep_time2 = dep_time %/% 100 * 60 + dep_time %% 100,
          arr_dep_diff = ifelse(arr_time2 < dep_time2, arr_time2-dep_time2 + 1440, arr_time2-dep_time2))
#if yes do one, if not do 2.
flights2

```

> I expect to see air_time and arr_time - dep_time are the same, but they are not the same. We can add a new `new_air_time = arr_time - dep_time`.

3.Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?
```{r}
transmute(flights,
  dep_time,
  dep_time_hour = dep_time %/% 100,
  dep_time_minute = dep_time %% 100,
  dep_time_min = (dep_time_hour * 60) + dep_time_minute,
  sched_dep_time,
  sched_dep_time_hour = sched_dep_time %/% 100,
  sched_dep_time_minute = sched_dep_time %% 100,
  sched_dep_time_min = (sched_dep_time_hour * 60) + sched_dep_time_minute,
  dep_delay,
  new_dep_delay = dep_time_min - sched_dep_time_min
  )

#
flights3 <- transmute(flights,
          dep_time, dep_time2 = dep_time %/% 100 * 60 + dep_time %% 100, 
          sched_dep_time, sched_dep_time2 = sched_dep_time %/% 100 * 60 + sched_dep_time %% 100, dep_delay, 
          dep_diff = ifelse(dep_time2+120 < sched_dep_time2, 
                            dep_time2-sched_dep_time2 + 1440,
                            dep_time2-sched_dep_time2
                            ))
flights3
ggplot(flights3, aes(x=dep_delay, y = dep_time2 - sched_dep_time2)) + geom_point(alpha=0.1)
ggplot(flights3, aes(x=dep_delay, y = dep_diff)) + geom_point(alpha=0.1)
```
> dep_delay = dep_time_min - sched_dep_time_min

4.Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().
```{r}
?min_rank()
delayrank <- mutate(flights,
          rank_delay = min_rank(desc(arr_delay))
          )
delayrank
arrange(delayrank, rank_delay)

flights %>% mutate(rank = min_rank(arr_delay)) %>% arrange(desc(rank)) %>% head(10)
```


5.What does 1:3 + 1:10 return? Why?
```{r}
1:3 + 1:10
```
> Because longer object length is not a multiple of shorter object length.

6.What trigonometric functions does R provide?

```{r}
help("Trig")
```

> cospi(x), sinpi(x), and tanpi(x), compute cos(pi*x), sin(pi*x), and tan(pi*x).
cos(x)
sin(x)
tan(x)

acos(x)
asin(x)
atan(x)
atan2(y, x)

cospi(x)
sinpi(x)
tanpi(x)
