---
title: "R-club-June-7"
author: "Min-Yao"
date: "2017年6月6日"
output: 
  html_document: 
    keep_md: yes
---

# 11 Data import

## 11.1 Introduction

### 11.1.1 Prerequisites

```{r}
library(tidyverse)
```


## 11.2 Getting started

```{r}
read_csv("a,b,c
1,2,3
4,5,6")

#1
read_csv("The first line of metadata
  The second line of metadata
  x,y,z
  1,2,3", skip = 2)

read_csv("# A comment I want to skip
  x,y,z
  1,2,3", comment = "#")

#2
read_csv("1,2,3\n4,5,6", col_names = FALSE)

read_csv("1,2,3\n4,5,6", col_names = c("x", "y", "z"))
```

```{r}
read_csv("a,b,c\n1,2,.", na = ".")
```


### 11.2.1 Compared to base R

### 11.2.2 Exercises

1.What function would you use to read a file where fields were separated with
“|”?
```{r}
#?read_delim()

read_delim ("1|2|3\n4|5|6", delim = "|", col_names = c("x", "y", "z"))

```

2.Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?

```{r}
?read_csv()
?read_tsv()
```

> read_csv2(file, col_names = TRUE, col_types = NULL,
  locale = default_locale(), na = c("", "NA"), quoted_na = TRUE,
  comment = "", trim_ws = TRUE, skip = 0, n_max = Inf,
  guess_max = min(1000, n_max), progress = interactive())

> read_tsv(file, col_names = TRUE, col_types = NULL,
  locale = default_locale(), na = c("", "NA"), quoted_na = TRUE,
  comment = "", trim_ws = TRUE, skip = 0, n_max = Inf,
  guess_max = min(1000, n_max), progress = interactive())

3.What are the most important arguments to read_fwf()?

```{r}
?read_fwf
```

> read_fwf(file, col_positions, col_types = NULL, locale = default_locale(),
  na = c("", "NA"), comment = "", skip = 0, n_max = Inf,
  guess_max = min(n_max, 1000), progress = interactive())

> fwf_empty(file, skip = 0, col_names = NULL, comment = "")

> fwf_widths(widths, col_names = NULL)

> fwf_positions(start, end, col_names = NULL)


4.Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?

```{r}
read_delim ("x,y\n1,'a,b'",quote = "'", delim = ",")

read_delim ("1,2,3\n'4,a','5,2','6,!'", quote = "'", delim = ",", col_names = c("x", "y", "z"))

```


5.Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

```{r}
read_csv("a,b\n1,2,3\n4,5,6")

```

> There are 2 columns in the first row, but 3 columns in the second and third rows.

```{r}
read_csv("a,b,c\n1,2\n1,2,3,4")
```

> There are 2 columns in the second row, but 3 columns in the first and 4 columns in the third rows.

```{r}
read_csv("a,b\n\"1")
```

> `\` need to be quoted

```{r}
read_csv("a,b\n1,2\na,b")
```

> `1` and `2` are characters.

```{r}
read_csv("a;b\n1;3")

read_csv2("a;b\n1;3")
```



## 11.3 Parsing a vector
```{r}
str(parse_logical(c("TRUE", "FALSE", "NA")))

str(parse_integer(c("1", "2", "3")))

str(parse_date(c("2010-01-01", "1979-10-14")))

str(parse_date(c("2010-01-01", "1979-10-14")))



```

### 11.3.1 Numbers

### 11.3.2 Strings

### 11.3.3 Factors

### 11.3.4 Dates, date-times, and times

### 11.3.5 Exercises

## 11.4 Parsing a file

### 11.4.1 Strategy

### 11.4.2 Problems

### 11.4.3 Other strategies

## 11.5 Writing to a file

## 11.6 Other types of data




