---
title: "Data transformation- continued"
author: "Min-Yao"
date: "2017年5月14日"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(nycflights13)
library(tidyverse)
library(Lahman)
```

## 5.6 Grouped summaries with summarise()

```{r}
summarise(flights, delay = mean(dep_delay, na.rm = TRUE))

by_day <- group_by(flights, year, month, day)
summarise(by_day, delay = mean(dep_delay, na.rm = TRUE))
```

### 5.6.1 Combining multiple operations with the pipe

```{r}
by_dest <- group_by(flights, dest)
delay <- summarise(by_dest,
  count = n(),
  dist = mean(distance, na.rm = TRUE),
  delay = mean(arr_delay, na.rm = TRUE)
)
delay <- filter(delay, count > 20, dest != "HNL")

ggplot(data = delay, mapping = aes(x = dist, y = delay)) +
  geom_point(aes(size = count), alpha = 1/3) +
  geom_smooth(se = FALSE)
```

```{r}
delays <- flights %>% 
  group_by(dest) %>% 
  summarise(
    count = n(),
    dist = mean(distance, na.rm = TRUE),
    delay = mean(arr_delay, na.rm = TRUE)
  ) %>% 
  filter(count > 20, dest != "HNL")
```

### 5.6.2 Missing values

```{r}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))

flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay, na.rm = TRUE))

not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))


```

### 5.6.3 Counts

```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay)
  )

ggplot(data = delays, mapping = aes(x = delay)) + 
  geom_freqpoly(binwidth = 10)
```

```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay, na.rm = TRUE),
    n = n()
  )

ggplot(data = delays, mapping = aes(x = n, y = delay)) + 
  geom_point(alpha = 1/10)
```

```{r}
delays %>% 
  filter(n > 25) %>% 
  ggplot(mapping = aes(x = n, y = delay)) + 
    geom_point(alpha = 1/10)
```

```{r}

batting <- as_tibble(Lahman::Batting)

batters <- batting %>% 
  group_by(playerID) %>% 
  summarise(
    ba = sum(H, na.rm = TRUE) / sum(AB, na.rm = TRUE),
    ab = sum(AB, na.rm = TRUE)
  )

batters %>% 
  filter(ab > 100) %>% 
  ggplot(mapping = aes(x = ab, y = ba)) +
    geom_point() + 
    geom_smooth(se = FALSE)

batters %>% 
  arrange(desc(ba))
```

### 5.6.4 Useful summary functions

```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    avg_delay1 = mean(arr_delay),
    avg_delay2 = mean(arr_delay[arr_delay > 0]) # the average positive delay
  )
```

```{r}
not_cancelled %>% 
  group_by(dest) %>% 
  summarise(distance_sd = sd(distance)) %>% 
  arrange(desc(distance_sd))
```

```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    first = min(dep_time),
    last = max(dep_time)
  )
```

```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    first_dep = first(dep_time), 
    last_dep = last(dep_time)
  )
```

```{r}
not_cancelled %>% 
  group_by(dest) %>% 
  summarise(carriers = n_distinct(carrier)) %>% 
  arrange(desc(carriers))
```

```{r}
not_cancelled %>% 
  count(dest)

not_cancelled %>%
  group_by(dest) %>%
  summarise(n=n())

```

```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(n_early = sum(dep_time < 500))

not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(hour_perc = mean(arr_delay > 60))
```

### 5.6.5 Grouping by multiple variables

```{r}
daily <- group_by(flights, year, month, day)
(per_day   <- summarise(daily, flights = n()))
(per_month <- summarise(per_day, flights = sum(flights)))
(per_year  <- summarise(per_month, flights = sum(flights)))
```

### 5.6.6 Ungrouping

```{r}
daily %>% 
  ungroup() %>%             # no longer grouped by date
  summarise(flights = n())  # all flights
```

### 5.6.7 Exercises

1.
```{r}
#1.1 A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>%
  group_by(flight) %>%
  summarize(early_15_min = mean(arr_delay <= -15), late_15_min = mean(arr_delay >= 15)) %>%
  filter(early_15_min == 0.5, late_15_min == 0.5)

#1.2 A flight is always 10 minutes late.

not_cancelled %>%
  group_by(flight) %>%
  summarize(late_10_min = mean(arr_delay == 10)) %>% 
  filter(late_10_min == 1)

#1.3 A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.

not_cancelled %>%
  group_by(flight) %>%
  summarize(early_30_min = mean(arr_delay <= -30), late_30_min = mean(arr_delay >= 30)) %>%
  filter(early_30_min == 0.5, late_30_min == 0.5)

#1.4 99% of the time a flight is on time. 1% of the time it’s 2 hours late.

not_cancelled %>%
  group_by(flight) %>%
  summarize(on_time = mean(arr_delay == 0), late_2_hr = mean(arr_delay >= 120)) %>%
  filter(on_time == 0.99, late_2_hr == 0.01)

```

2.Come up with another approach that will give you the same output as not_cancelled %>% count(dest) and not_cancelled %>% count(tailnum, wt = distance) (without using count()).
```{r}
not_cancelled %>% count(dest)

not_cancelled %>%
  group_by(dest) %>%
  summarise(n=n())

not_cancelled %>% count(tailnum, wt = distance)

not_cancelled %>%
  group_by(tailnum) %>%
  summarize(n = sum(distance))
```

3. Our definition of cancelled flights (is.na(dep_delay) | is.na(arr_delay) ) is slightly suboptimal. Why? Which is the most important column?

> For cancelled flights, dep_delay is the most important column.
If there is a flight accident, we only have dep_delay but no arr_delay.

4. Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?

```{r}
flights %>%
  group_by(year, month, day) %>%
  summarize(canceled_prop = mean(is.na(dep_delay)),
            avg_delay = mean(dep_delay, na.rm = TRUE)) %>%
  arrange(desc(avg_delay)) %>%
  ggplot(mapping = aes(x = canceled_prop, y = avg_delay)) +
  geom_point(alpha = 0.3)

```

5. Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))

```{r}
not_cancelled %>%
  group_by(carrier, dest) %>%
  summarize(mean_delay = mean(arr_delay))%>%
  arrange(desc(mean_delay))

not_cancelled %>%
  group_by(carrier) %>%
  summarize(mean_delay = mean(arr_delay)) %>%
  arrange(desc(mean_delay))

not_cancelled %>%
  group_by(dest) %>%
  summarize(mean_delay = mean(arr_delay)) %>%
  arrange(desc(mean_delay))
```


6. What does the sort argument to count() do. When might you use it?

```{r}
?count()
?sort
```

> Sort (or order) a vector or factor (partially) into ascending or descending order. For ordering along more than one variable, e.g., for sorting data frames.



## 5.7 Grouped mutates (and filters)

```{r}
flights_sml <- select(flights, 
  year:day, 
  ends_with("delay"), 
  distance, 
  air_time
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  speed = distance / air_time * 60
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)

flights_sml %>% 
  group_by(year, month, day) %>%
  filter(rank(desc(arr_delay)) < 10)
```

```{r}
popular_dests <- flights %>% 
  group_by(dest) %>% 
  filter(n() > 365)
popular_dests
```

```{r}
popular_dests %>% 
  filter(arr_delay > 0) %>% 
  mutate(prop_delay = arr_delay / sum(arr_delay)) %>% 
  select(year:day, dest, arr_delay, prop_delay)
```

### 5.7.1 Exercises
1. Refer back to the lists of useful mutate and filtering functions. Describe how each operation changes when you combine it with grouping.

```{r}
?mutate()
?filter()
```


2. Which plane (tailnum) has the worst on-time record? N384HA
```{r}
flights %>% 
  group_by(tailnum) %>%
  filter(rank(desc(arr_delay)) < 10) %>%
  arrange(desc(arr_delay))
```

3.What time of day should you fly if you want to avoid delays as much as possible?

```{r}
not_cancelled %>%
  group_by(hour) %>%
  summarize(arr_delay = sum(arr_delay)) %>%
  ggplot(aes(x = hour, y = arr_delay)) +
  geom_col()
```


4.For each destination, compute the total minutes of delay. For each, flight, compute the proportion of the total delay for its destination.

```{r}
not_cancelled %>%
  group_by(dest) %>%
  mutate(total_flight_delay = sum(arr_delay), prop_delay = arr_delay/sum(arr_delay)) %>%
  arrange(desc(prop_delay))
  

##
not_cancelled %>% group_by(dest) %>%
  mutate(total_delay = sum(arr_delay)) %>%
  group_by(flight, carrier) %>%
  mutate(proportion_delay = arr_delay / total_delay) %>%
  arrange(dest,desc(proportion_delay)) %>% select(dest,flight,total_delay, proportion_delay)

```


5.Delays are typically temporally correlated: even once the problem that caused the initial delay has been resolved, later flights are delayed to allow earlier flights to leave. Using lag() explore how the delay of a flight is related to the delay of the immediately preceding flight.

```{r}
?flights

not_cancelled %>%
  group_by(origin, year, month, day) %>%
  arrange(origin, year, month, day, hour, minute) %>%
  mutate(preceding_flight_delay = lag(dep_delay)) %>%
  ggplot(aes(x = preceding_flight_delay, y = dep_delay)) +
  geom_point() + geom_smooth()
```


6.Look at each destination. Can you find flights that are suspiciously fast? (i.e. flights that represent a potential data entry error). Compute the air time a flight relative to the shortest flight to that destination. Which flights were most delayed in the air?

```{r}
not_cancelled %>%
  group_by(dest) %>%
  mutate(shortest_flight = min(air_time)) %>%
  arrange(dest, air_time)
```


7.Find all destinations that are flown by at least two carriers. Use that information to rank the carriers.

```{r}
not_cancelled %>%
  group_by(dest, carrier) %>%
  count(carrier) %>%
  filter(n >= 2)

```


8.For each plane, count the number of flights before the first delay of greater than 1 hour.

```{r}
not_cancelled %>%
  group_by(tailnum) %>%
  arrange(year, month, day, hour) %>%
  summarise(less_one_late = sum(arr_delay < 60))
```

jrnold.github.io

# ctrl+shift+M = %>%
# n_distinct()
