---
title: "R-club-June-14"
author: "Min-Yao"
date: "2017年6月13日"
output: 
  html_document: 
    keep_md: yes
---

# 12 Tidy data

## 12.1 Introduction

### 12.1.1 Prerequisites

```{r}
library(tidyverse)
library(ggplot2)
```


## 12.2 Tidy data

```{r}
table1
table2
table3
table4a
table4b

table1 %>% 
  mutate(rate = cases / population * 10000)
table1 %>% 
  count(year, wt = cases)

ggplot(table1, aes(year, cases)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))

```

### 12.2.1 Exercises

1.Using prose, describe how the variables and observations are organised in each of the sample tables.

> Table 1: each variable is in a column.

> 

> 

> 


2.Compute the rate for table2, and table4a + table4b. You will need to perform four operations:

Extract the number of TB cases per country per year.
Extract the matching population per country per year.
Divide cases by population, and multiply by 10000.
Store back in the appropriate place.
Which representation is easiest to work with? Which is hardest? Why?

3.Recreate the plot showing change in cases over time using table2 instead of table1. What do you need to do first?


## 12.3 Spreading and gathering

### 12.3.1 Gathering

### 12.3.2 Spreading

### 12.3.3 Exercises

## 12.4 Separating and uniting

### 12.4.1 Separate

### 12.4.2 Unite

### 12.4.3 Exercises

