---
title: "R-club-June-14"
author: "Min-Yao"
date: "2017年6月13日"
output: 
  html_document: 
    keep_md: yes
---

# 12 Tidy data

## 12.1 Introduction

### 12.1.1 Prerequisites

```{r}
library(tidyverse)
library(ggplot2)
```


## 12.2 Tidy data

```{r}
table1
table2
table3
table4a
table4b

table1 %>% 
  mutate(rate = cases / population * 10000)
table1 %>% 
  count(year, wt = cases)

ggplot(table1, aes(year, cases)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))

```

### 12.2.1 Exercises

1.Using prose, describe how the variables and observations are organised in each of the sample tables.

> Table 1: each variable is in a column. Each observation have its own row.

> Table 2: type is nested in year and country

> Table 3: rate column is calculated from 2 variable (cases / population)

> Table 4: Spread across two tibbles, table4a is cases and table4b is population data.


2.Compute the rate for table2, and table4a + table4b. You will need to perform four operations:

Extract the number of TB cases per country per year.
Extract the matching population per country per year.
Divide cases by population, and multiply by 10000.
Store back in the appropriate place.

```{r}
#T2
T2cases <- table2 %>%
  group_by(country, year) %>%
   filter(type == "cases")
T2cases
T2population <- table2 %>%
  group_by(country, year) %>%
   filter(type == "population")
T2population

newT2 <- bind_cols(T2cases[, c(1:2,4)], T2population[, 4])
newT2
colnames(newT2)[3:4] <- c("cases", "population")
newT2

finalT2 <- newT2 %>%
  mutate(rates = cases / population * 10000)
finalT2

#T4
newT4 <- bind_cols(table4a, table4b[, 2:3])
newT4
colnames(newT4)[2:5] <- c("cases1999", "cases2000", "pop1999", "pop2000")
newT4

finalT4 <- newT4 %>%
  mutate( rate1999 = cases1999 / pop1999 * 10000,
          rate2000 = cases2000 / pop2000 * 10000)
finalT4


```


Which representation is easiest to work with? Which is hardest? Why?

> T1 is easiest to work with. T2 is hardest to work with.

3.Recreate the plot showing change in cases over time using table2 instead of table1. What do you need to do first?

```{r}
#T1
ggplot(table1, aes(year, cases)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))

#T2
T2cases <- table2 %>%
  group_by(country, year) %>%
   filter(type == "cases")
T2cases
ggplot(T2cases, aes(year, count)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))
```

> I need to do filter first.

## 12.3 Spreading and gathering

### 12.3.1 Gathering

```{r}
table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases")
table4b %>% 
  gather(`1999`, `2000`, key = "year", value = "population")

tidy4a <- table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases")
tidy4b <- table4b %>% 
  gather(`1999`, `2000`, key = "year", value = "population")
left_join(tidy4a, tidy4b)


```

### 12.3.2 Spreading

```{r}
table2
spread(table2, key = type, value = count)

```

### 12.3.3 Exercises

1.Why are gather() and spread() not perfectly symmetrical?
Carefully consider the following example:

```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)
stocks
stocks %>% 
  spread(year, return) %>% 
  gather("year", "return", `2015`:`2016`)
```

(Hint: look at the variable types and think about column names.)

> column type information of `year` change from <dbl> to <chr>

Both spread() and gather() have a convert argument. What does it do?

```{r}
#?spread
#?gather

```

> spread {tidyr} convert	
If TRUE, type.convert with asis = TRUE will be run on each of the new columns. This is useful if the value column was a mix of variables that was coerced to a string. If the class of the value column was factor or date, note that will not be true of the new columns that are produced, which are coerced to character before type conversion.

> gather {tidyr} convert	
If TRUE will automatically run type.convert on the key column. This is useful if the column names are actually numeric, integer, or logical.


2. Why does this code fail?

```{r}
table4a
#table4a %>% 
#  gather(1999, 2000, key = "year", value = "cases")

#> Error in combine_vars(vars, ind_list): Position must be between 0 and n

table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases")

```

>  “1999” and “2000” are non-syntactic names (because they don’t start with a letter) so we have to surround them in backticks.

3. Why does spreading this tibble fail? How could you add a new column to fix the problem?

```{r}
people <- tribble(
  ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)
people

#spread(people, key, value)

people2 <- tribble(
  ~name,             ~key,    ~value, ~rep,
  #-----------------|--------|------|------
  "Phillip Woods",   "age",       45, 1,
  "Phillip Woods",   "height",   186, 1,
  "Phillip Woods",   "age",       50, 2,
  "Jessica Cordero", "age",       37, 1,
  "Jessica Cordero", "height",   156, 1
)
people2

spread(people2, key, value)


```

> Error: Duplicate identifiers for rows (1, 3)


4. Tidy the simple tibble below. Do you need to spread or gather it? What are the variables?

```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
preg

gather(preg, male, female, key = "gender", value = "number")

```


## 12.4 Separating and uniting

### 12.4.1 Separate

```{r}
table3

table3 %>% 
  separate(rate, into = c("cases", "population"))

table3 %>% 
  separate(rate, into = c("cases", "population"), sep = "/")

table3 %>% 
  separate(rate, into = c("cases", "population"), convert = TRUE)

table3 %>% 
  separate(year, into = c("century", "year"), sep = 2)

```

### 12.4.2 Unite

```{r}
table5

table5 %>% 
  unite(new, century, year)

table5 %>% 
  unite(new, century, year, sep = "")

```


### 12.4.3 Exercises

1. What do the extra and fill arguments do in separate()? Experiment with the various options for the following two toy datasets.

```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"))
#Too many values at 1 locations: 2

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"))
#Too few values at 1 locations: 2

#?separate

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "drop")
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "merge")

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "right")
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "left")

```

> extra	
If sep is a character vector, this controls what happens when there are too many pieces. There are three valid options:
"warn" (the default): emit a warning and drop extra values.
"drop": drop any extra values without a warning.
"merge": only splits at most length(into) times

> fill	
If sep is a character vector, this controls what happens when there are not enough pieces. There are three valid options:
"warn" (the default): emit a warning and fill from the right
"right": fill with missing values on the right
"left": fill with missing values on the left

2. Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?

```{r}
#?unite
#?separate

table5 %>% 
  unite(new, century, year, sep = "", remove = F)

table3 %>% 
  separate(rate, into = c("cases", "population"), sep = "/", remove = F)
```

> separate {tidyr} remove	
If TRUE, remove input column from output data frame.

> unite {tidyr} remove	
If TRUE, remove input columns from output data frame.


3. Compare and contrast separate() and extract(). Why are there three variations of separation (by position, by separator, and with groups), but only one unite?

```{r}
#?separate
#?extract

```

> extract {tidyr} Extract one column into multiple columns.
Description
Given a regular expression with capturing groups, extract() turns each group into a new column. If the groups don't match, or the input is NA, the output will be NA.

```{r}
df <- data.frame(x = c(NA, "a-b", "a-d", "b-c", "d-e"))
df
df %>% extract(x, "A")
df %>% extract(x, c("A", "B"), "([[:alnum:]]+)-([[:alnum:]]+)")
```

> separate {tidyr} Separate one column into multiple columns.


