---
title: "Apr-26-ggplot"
author: "Min-Yao"
date: "2017年4月25日"
output: 
  html_document: 
    keep_md: yes
---

# 3 Data visualisation

## 3.1 Introduction

### 3.1.1 Prerequisites

## 3.2 First steps

### 3.2.1 The mpg data frame

### 3.2.2 Creating a ggplot

### 3.2.3 A graphing template


```{r}
library(tidyverse)

mpg
?mpg

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

#ggplot(data = <DATA>) + 
#  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))

```

### 3.2.4 Exercises
```{r}
#1
ggplot(data = mpg)

#2
mtcars

#3
?mpg

#4
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = hwy, y = cyl))

#5
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = class, y = drv))
```


>2. 1-10 of 32 rows | 1-10 of 11 columns

>3. drv: f = front-wheel drive, r = rear wheel drive, 4 = 4wd

>4. cyl: number of cylinders, hwy: highway miles per gallon

>5. class: "type" of car, drv: f = front-wheel drive, r = rear wheel drive, 4 = 4wd


## 3.3 Aesthetic mappings
```{r}

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))

#
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

#in class notes
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class == "compact"))

#in class notes 2
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class == "compact")) +
  labs(color = "Type") +
  scale_color_manual(labels = c("Not Compact", "Compact"), 
                     values = c("red","blue"))

```


### 3.3.1 Exercises
```{r}
#in class notes
# we can use ```{r, fig.width = 6, fig.height=6} to change size of the plots
#1
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

#2
?mpg
mpg

#3
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cty))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = cty))

#ggplot(data = mpg) + 
#  geom_point(mapping = aes(x = displ, y = hwy, shape = cty))

#4
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cty, size = cty))

#5
?geom_point
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), shape = 2, stroke = 3)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), shape = 2, size = 3)

#6
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5))

```

>1. Parenthesis is at the wrong location.

>2. manufacturer, model, year, cyl, trans, drv, fl, and class are categorical. displ, cty, hwy are continuous.

>3. A continuous variable can not be mapped to shape

>4. I can map the same variable to color and size.

>5. Use the stroke aesthetic to modify the width of the border. change size. dots

## 3.4 Common problems

## 3.5 Facets

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2) +
  facet_grid(. ~ cyl)

```


### 3.5.1 Exercises
```{r}
#1
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ cty, nrow = 2)

# in class notes:
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ cty, scales= "free")

# neated
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ cty + year)

#2
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)

#3
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)

#4
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

#5
?facet_wrap

```

>2. No data points when drv = r and cyl = 4 and 5, and drv = 4 and cyl = 5. It's overplotting in `ggplot(data = mpg) + geom_point(mapping = aes(x = drv, y = cyl))`! which means that they are overlap with each other.

>3. Change the `.` position will change faceting in the rows or columns dimension.

>4. Using faceting instead of the colour aesthetic can see the dot pattern easier. The disadvantages are much more plots. If I had a larger dataset, 
too many point (classes) so we cannot see the data clearly

>5. The `nrow` and `ncol` = Number of rows and columns. Other options control the layout of the individual panels: dir, facet_grid(). Because the argument of facet_grid() facet in the rows or columns dimension.

>6. We can see the whole picture much easlier without scrolling down because it fits the screen, so we should put the variable with more unique levels in the columns.



