---
title: "Apr-26-ggplot"
author: "Min-Yao"
date: "2017年4月25日"
output: 
  html_document: 
    keep_md: yes
---

#3 Data visualisation
```{r}
library(tidyverse)

mpg
?mpg

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

#ggplot(data = <DATA>) + 
#  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))

```

#3.2.4 Exercises
```{r}
#1
ggplot(data = mpg)

#2
mtcars

#3
?mpg

#4
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = hwy, y = cyl))

#5
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = class, y = drv))
```


>2. 1-10 of 32 rows | 1-10 of 11 columns

>3. drv: f = front-wheel drive, r = rear wheel drive, 4 = 4wd

>4. cyl: number of cylinders, hwy: highway miles per gallon

>5. class: "type" of car, drv: f = front-wheel drive, r = rear wheel drive, 4 = 4wd


#3.3 Aesthetic mappings
```{r}

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))

#
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```


#3.3.1 Exercises
```{r}
#1
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

#2
?mpg
mpg

#3
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cty))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = cty))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = cty))

#4
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cty, size = cty))

#5
?geom_point
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, stroke = 3))

#6
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5))

```

>1. Parenthesis is at wrong location.

>2. manufacturer, model, year, cyl, trans, drv, fl, and class are categorical. displ, cty, hwy are continuous.

>3. A continuous variable can not be mapped to shape

>4. map the same variable to color and size.

>5. change size. dots









